### 2014-09-18 dicook/school_start_age.Rmd
slides of material in paper

# To get a blank background on map
new_theme_empty <- theme_bw()
new_theme_empty$line <- element_blank()
new_theme_empty$rect <- element_blank()
new_theme_empty$strip.text <- element_blank()
new_theme_empty$axis.text <- element_blank()
new_theme_empty$plot.title <- element_blank()
new_theme_empty$axis.title <- element_blank()
new_theme_empty$plot.margin <- structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit")
```
```
```{r age, fig.width=8, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub <- student2012[, c(1, 6, 12, 14, 501, 541, 546, 634)]
colnames(student2012.sub)[1] <- "name"
# Now add data
student2012.sub$name <- as.character(student2012.sub$name)
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Perm(Russian Federation)"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"
student2012.sub$name[student2012.sub$name=="China-Macau"] <- "China"
student2012.sub$name[student2012.sub$name=="Connecticut (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Florida (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Massachusetts (USA)"] <- "United States of America"
student2012.sub$ST06Q01 <- as.numeric(student2012.sub$ST06Q01)
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1READ <- as.numeric(student2012.sub$PV1READ)
student2012.sub$PV1SCIE <- as.numeric(student2012.sub$PV1SCIE)
student2012.sub$SENWGT_STU <- as.numeric(student2012.sub$SENWGT_STU)
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  math4 = mean(PV1MATH[ST06Q01 == 4], na.rm = T), 
                  math5 = mean(PV1MATH[ST06Q01 == 5], na.rm = T), 
                  math6 = mean(PV1MATH[ST06Q01 == 6], na.rm = T), 
                  math7 = mean(PV1MATH[ST06Q01 == 7], na.rm = T), 
                  math8 = mean(PV1MATH[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Math Score", 
      geom=c("point","smooth"), se=F, group=name) + 
 facet_wrap(~name, ncol=8) + theme_bw() 
# ggsave("school-start.pdf", width=14, height=14)
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  read4 = mean(PV1READ[ST06Q01 == 4], na.rm = T), 
                  read5 = mean(PV1READ[ST06Q01 == 5], na.rm = T), 
                  read6 = mean(PV1READ[ST06Q01 == 6], na.rm = T), 
                  read7 = mean(PV1READ[ST06Q01 == 7], na.rm = T), 
                  read8 = mean(PV1READ[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Reading Score", 
      geom=c("point","smooth"), se=F, group=name) + 
 facet_wrap(~name, ncol=8) + theme_bw() 
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  scie4 = mean(PV1SCIE[ST06Q01 == 4], na.rm = T), 
                  scie5 = mean(PV1SCIE[ST06Q01 == 5], na.rm = T), 
                  scie6 = mean(PV1SCIE[ST06Q01 == 6], na.rm = T), 
                  scie7 = mean(PV1SCIE[ST06Q01 == 7], na.rm = T), 
                  scie8 = mean(PV1SCIE[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Science Score", 
      geom=c("point","smooth"), se=F, group=name) + 
 facet_wrap(~name, ncol=8) + theme_bw() 
````

>>>>

# To get a blank background on map
new_theme_empty <- theme_bw()
new_theme_empty$line <- element_blank()
new_theme_empty$rect <- element_blank()
new_theme_empty$strip.text <- element_blank()
new_theme_empty$axis.text <- element_blank()
new_theme_empty$plot.title <- element_blank()
new_theme_empty$axis.title <- element_blank()
new_theme_empty$plot.margin <- structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit")
```

```{r age, fig.width=8, fig.height=12, warning=FALSE, message=FALSE}
student2012.sub <- student2012[, c(1, 6, 12, 14, 501, 541, 546, 634)]
colnames(student2012.sub)[1] <- "name"
# Now add data
student2012.sub$name <- as.character(student2012.sub$name)
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Perm(Russian Federation)"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"
student2012.sub$name[student2012.sub$name=="China-Macau"] <- "China"
student2012.sub$name[student2012.sub$name=="Connecticut (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Florida (USA)"] <- "United States of America"
student2012.sub$name[student2012.sub$name=="Massachusetts (USA)"] <- "United States of America"
student2012.sub$ST06Q01 <- as.numeric(student2012.sub$ST06Q01)
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1READ <- as.numeric(student2012.sub$PV1READ)
student2012.sub$PV1SCIE <- as.numeric(student2012.sub$PV1SCIE)
student2012.sub$SENWGT_STU <- as.numeric(student2012.sub$SENWGT_STU)
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  math4 = mean(PV1MATH[ST06Q01 == 4], na.rm = T), 
                  math5 = mean(PV1MATH[ST06Q01 == 5], na.rm = T), 
                  math6 = mean(PV1MATH[ST06Q01 == 6], na.rm = T), 
                  math7 = mean(PV1MATH[ST06Q01 == 7], na.rm = T), 
                  math8 = mean(PV1MATH[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Math Score", 
      geom=c("point","smooth"), se=F, group=name) + 
 facet_wrap(~name, ncol=8) + theme_bw() 
# ggsave("school-start.pdf", width=14, height=14)
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  read4 = mean(PV1READ[ST06Q01 == 4], na.rm = T), 
                  read5 = mean(PV1READ[ST06Q01 == 5], na.rm = T), 
                  read6 = mean(PV1READ[ST06Q01 == 6], na.rm = T), 
                  read7 = mean(PV1READ[ST06Q01 == 7], na.rm = T), 
                  read8 = mean(PV1READ[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Reading Score", 
      geom=c("point","smooth"), se=F, group=name) + 
 facet_wrap(~name, ncol=8) + theme_bw() 
student2012.sub.age <- summarise(group_by(student2012.sub, name), 
                  scie4 = mean(PV1SCIE[ST06Q01 == 4], na.rm = T), 
                  scie5 = mean(PV1SCIE[ST06Q01 == 5], na.rm = T), 
                  scie6 = mean(PV1SCIE[ST06Q01 == 6], na.rm = T), 
                  scie7 = mean(PV1SCIE[ST06Q01 == 7], na.rm = T), 
                  scie8 = mean(PV1SCIE[ST06Q01 >  7], na.rm = T))
student2012.sub.age.m <- melt(student2012.sub.age)
student2012.sub.age.m$variable <- substr(student2012.sub.age.m$variable, 5, 5)
student2012.sub.age.m$variable <- as.numeric(student2012.sub.age.m$variable)
qplot(variable, value, data=student2012.sub.age.m, xlab="Age at start", ylab="Science Score", 
      geom=c("point","smooth"), se=F, group=name) + 
 facet_wrap(~name, ncol=8) + theme_bw() 
````
